Distributional Trees for Circular Data

### 2019-02-07 pkg/disttree/inst/IWSM2019/abstract_IWSM2019_schlosser.tex
adapted names of covariates
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2451 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 075eeb86197634ee8c5ec854f61125cb34819c46

\begin{figure}[p!]\centering
\includegraphics[height = .5\textheight,angle=90,origin=c]{schlosser-circtree_plot.pdf}
\caption{Fitted tree based on the von Mises distribution for wind direction forecasting.
In each terminal node the empirical histogram (gray) and fitted density (red line)
are depicted along with the estimated location parameter (red hand). The covariates
employed are wind direction ($\text{degree}$), wind speed ($\text{ms}^{-1}$),
and pressure gradients ($\text{hPa}$) west and east of the airport,
all lagged by one hour.}
\label{schlosser:fig_tree} \end{figure}

>>>>

\begin{figure}[p!]\centering
\includegraphics[height = .5\textheight,angle=90,origin=c]{schlosser-circtree_plot.pdf}
\caption{Fitted tree based on the von Mises distribution for wind direction forecasting.
In each terminal node the empirical histogram (gray) and fitted density (red line)
are depicted along with the estimated location parameter (red hand). The covariates
employed are wind direction (degree), wind speed ($\text{ms}^{-1}$),
and pressure gradients ($\text{dpressure; hPa}$) west and east of the airport,
all lagged by one hour.}
\label{schlosser:fig_tree} \end{figure}
